Practical Optional Types for Clojure

### 2015-07-10 formal-model.tex
move typing rules to figures

\paragraph{Logical formulas over type environments}
Standard type systems use type environments to track lexical type information.
Introducing a lexically scoped variable $x$ is a matter of associating 
associating $x$ with its type $\Number$ (a number) in the type environment.
Correspondingly, checking the type of a variable is a simple map lookup.
$$
\begin{array}{lr}
\judgementtwo{\x{} \mapsto \Number}{\appexp{\inc{}}{\x{}}}{\Number}
&
\infer [LC-Local]
{ {\propenv{}}(\x{}) = {\t{}}
}
{ \judgementtwo {\propenv{}} 
            {\x{}} {\t{}}
           }
\end{array}
$$

Occurrence typing takes a different approach.
The same information is conveyed by \emph{logical formulas}.
The logical statement {\isprop{\Number{}}{\x{}}} says the value
obtained via $x$ is of type \Number{}. We now must \emph{prove}
a variable's type via a \emph{logical system}.
$$
\begin{array}{lr}
\judgementtwo{\isprop{\Number{}}{\x{}}}{\appexp{\inc{}}{\x{}}}{\Number}
&
\infer [T-LocalProve]
{ \inpropenv {\propenv{}} {\isprop {\t{}} {\x{}}}}
{ \judgementtwo {\propenv{}} 
            {\x{}} {\t{}}
           }
\end{array}
$$
The proof system judgment { \inpropenv {\propenv{}} {\isprop {\t{}} {\x{}}}}
says logical assumptions {\propenv{}} prove variable \x{} is of type \t{}.

\paragraph{Symbolic representations}
As we saw in \secref{sec:overview},
occurrence typing is capable of reasoning
about deeply nested expressions.
For each expression, the type system assigns a symbolic representation
with respect to the current lexical environment. For example,

\begin{itemize}
  \item $x$ is represented as $x$; 
  \item $\appexpone{\ccclass{\appexp{\makekw{lunch}}{m}}}$ is represented as ${\path{\classpe{}}{\path{\keype{\makekw{lunch}}}{m}}}$;
  \item $42$ has no representation, called \emptyobject{}.
\end{itemize}

This symbolic representation is called the expression's \emph{object}. 
\figref{main:figure:termsyntax} gives the syntax for objects.
\emptyobject{} is the
\emph{empty object}. Non-empty objects \path{\pathelem{}}{\x{}} consist of a symbol \x{} and a \emph{path} \pathelem{},
which is a possibly-empty sequence of \emph{path elements} applied right-to-left.
This paper uses two path elements---{\classpe{}} and {\keype{k}}---representing a call to \classconst{} and
a keyword lookup on $k$ respectively.

@@

\paragraph{Logical statements about objects}
So far we have seen logical statements about the simplest object, a variable---{\isprop{\t{}}{\x{}}},
saying variable \x{} is of type \t{}.
We extend logical statements to reason about \emph{arbitrary} non-empty 
objects {\isprop{\t{}}{\path{\pathelem{}}{\x{}}}}.

To illustrate, recall \egref{example:desserts-on-meal}.
We know the parameter $o$ is of type $\Order$
by the annotation on $desserts$---written
\begin{equation}
\qquad {\isprop{\Order}{o}}
\end{equation}
as a logical statement.
%
In checking the ${\makekw{combo}}$ method, we also assume
${\appexp{\makekw{Meal}}{o}}$ is ${\makekw{combo}}$,
based on multimethod dispatch rules. This is written
\begin{equation}
  \qquad {\isprop{\Value{\makekw{combo}}}{\path{\keype{\makekw{Meal}}}{o}}}
\end{equation}
and pronounced ``the ${\makekw{Meal}}$ path of variable $o$ is of type
{\Value{\makekw{combo}}}'', a keyword singleton type.

\paragraph{Logical system in action} At some point in checking the {\makekw{combo}} method,
we will need the type of $o$.
Our proposition environment consists of both above facts
$$
\propenv{} = {{\isprop{\Order}{o}},
    {\isprop{\Value{\makekw{combo}}}{\path{\keype{\makekw{Meal}}}{o}}}}
$$
and T-LocalProve says $o$ is of type \t{} if \propenv{} \emph{proves} $o$ is of type \t{}
$$
{ \inpropenv 
  {\propenv{}}
  {\isprop {\t{}} {o}}}
$$
The logical system deduces \t{} as being a {\makekw{combo}} meal.

Now the purpose of a logical representation can be conveyed---we rely on the logical
system to combine pieces of type information to deduce more accurate types for lexical
bindings.

\paragraph{Extension to propositional logic}
The kinds of logical statements are extended to \emph{propositional logic}.
\figref{main:figure:termsyntax} describes the syntax we will use for the rest of the paper.
The proposition metavariable \prop{} 
consists of positive and negative \emph{type propositions} 
about non-empty objects---{\isprop {\t{}} {\path {\pathelem{}} {\x{}}}}
and {\notprop {\t{}} {\path {\pathelem{}} {\x{}}}}
respectively---the former we have seen before, 
the latter pronounced ``the object {\path {\pathelem{}} {\x{}}} is \emph{not} of type \t{}''.
The other propositions are standard logical connectives: implications, conjunctions,
disjunctions, and the trivial (\topprop{}) and impossible (\botprop{}) propositions.

@@

The pair of propositions {\filterset{\thenprop{\prop{}}}{\elseprop{\prop{}}}} is called a \emph{proposition set}.

@@

\paragraph{Elimination rule for propositions}
We can now review the main elimination rule for propositions, T-Local.
$$
    {\TLocal}
$$
It says, if proposition environment \propenv{} proves variable \x{} is 
of type \t{}, then under proposition environment \propenv{}
variable \x{} is of type \t{}. Also, if \x{} is a true value, then
we know \x{} is neither \False or \Nil, and if \x{} is a false value,
then \x{} is either \False or \Nil. Finally, the symbolic representation
for \x{}---its object---is \x{}.

\paragraph{Introduction rules for propositions}
Every program branch is an opportunity to extend the proposition environment
since we learn whether a test expression evaluates true or false. The T-If
rule assumes the test's `then' proposition \thenprop{\prop{1}}
in the then branch, and the test's `else' proposition \elseprop{\prop{1}}
in the else branch.
\begin{mathpar}
  {\TIf}
\end{mathpar}
The `then' proposition is {\orprop {\thenprop {\prop{2}}} {\thenprop {\prop{3}}}}
because if the entire expression reduces to a true value,
then either the `then' branch is true---implying {\thenprop {\prop{2}}}---or
the `else' branch is true---implying {\thenprop {\prop{3}}}.

@@

@@

The introduction rule for lambda abstractions also introduces 
propositions to bring its parameter into scope when checking the body.
The proposition set says lambda expressions cannot be false.
$$
{\TAbs}
$$
The object \x{} is in scope in the latent propositions \thenprop{\prop{}} and
\elseprop{\prop{}}, latent object \object{}, and latent type \t{}. These are substituted with the
actual argument object---\objectp{}---with the application rule for functions.
$$
    {\TApp}
$$

The rule for let expressions links inferred information about
\x{} to the expression used to instantiate \x{}, \ep{1}, via logical implications.
$$
%\footnotesize
\infer [T-Let]
{ \judgementrewrite {\propenv{}} {\e{1}} {\s{}} {\filterset {\thenprop {\prop{1}}} {\elseprop {\prop{1}}}}
             {\object{1}}
             {\ep{1}}
             \\\\
             \propp{} = {\impprop {\notprop {\falsydiff{}} {\x{}}} {\thenprop {\prop{1}}}}
             \\\\
             \proppp{} = {\impprop {\isprop {\falsydiff{}} {\x{}}} {\elseprop {\prop{1}}}}
  \\\\
  \judgementrewrite
       {\propenv{}, {\isprop {\s{}} {\x{}}},
         {\propp{}},
         {\proppp{}}}
             {\e{}} {\t{}} {\filterset {\thenprop {\prop{}}} {\elseprop {\prop{}}}}
             {\object{}} 
             {\ep{}}
             }
{ \judgementrewrite {\propenv{}} {\letexp {\x{}} {\e{1}} {\e{}}} {\t{}}
             {\replacefor {\filterset {\thenprop {\prop{}}} {\elseprop {\prop{}}}}
                          {\object{1}}
                          {\x{}}}
             {\replacefor {\object{}} 
                          {\object{1}}
                          {\x{}}}
             {\letexp {\x{}} {\ep{1}} {\ep{}}}
             }
$$

\paragraph{Other typing rules} The remaining core typing rules
include a subsumption rule, and rules for other values that reflect
\nil{} and \false{} as being the only false values.
$$
\footnotesize
    %{\TDo}
    %{\TClass}
    %{\TIf}
    %{\TAbs}
    %\begin{array}{c}
    %  {\TSubsume}\\\\
    %  {\TNum}
    %\end{array}
    \begin{array}{c}
      {\TNum}\\\\
      {\TConst}\\\\
      {\TKw}\\\\
      {\TClass}\\\\
      {\TTrue}\\\\
    \end{array}
    \begin{array}{c}
      {\TSubsume}\\\\
      {\TStr}\\\\
      {\TNil}\\\\
      {\TFalse}
    \end{array}
$$

@@

\paragraph{Subtyping}
\figref{main:figure:subtyping} presents subtyping
as a reflexive and transitive relation with top type \Top. 
Singleton types are instances of their respective classes---boolean singleton types
are of type \Boolean{}, class literals are instances of \Class{} and keywords are
instances of \Keyword{}.
Instances of classes \class{} are subtypes of \Object{}. Since function types 
are subtypes of \IFn{}, all types except for \Nil{} are subtypes of \Object{},
so \Top{} = {\Union{\Nil}{\Object}}.
Function subtyping is contravariant left of the arrow---latent propositions, object
and the result type are covariant.
Subtyping for untagged unions is standard.

\paragraph{class} The \classconst{} function is implemented as a constant
function (via T-Const), which returns a latent object which is the argument applied to the
\classpe{} path element
$$
\constanttypefigure{}
$$
The dynamic semantics are given in \figref{main:figure:primitivesem}.
%The definition of \updateliteral{} supports various idioms relating to \classpe{}
%which we introduce in \secref{sec:isaformal}.

@@

\paragraph{Constructors} First we check and convert {\newexp {\File{}} {\makestr{a/b}}} to {\newstaticexp {\String} {\File{}} {\File{}} {\makestr{a/b}}}
The T-New typing rule checks and rewrites constructors.
$$
    {\TNew}
$$
To check
{\newexp {\File{}} {\makestr{a/b}}}
we first resolve the constructor overload in the class table---there is at most one
to simplify presentation.
With \classhint{1} = \String,
we convert to a nilable type the argument with \t{1} = \Union{\Nil}{\String}
and type check {\makestr{a/b}} against \t{1}.
Typed Clojure defaults to allowing non-nilable arguments, but this
can be overridden, so we model the more general case.
% which erases nil
The return Java type \File is converted to a non-nil
Typed Clojure type \t{} = \File for the return type,
and the proposition set says constructors can never be false---constructors
can never produce the internal boolean value that Clojure uses for \false{}, or \nil{}.
Finally, the constructor rewrites to {\newstaticexp {\String} {\File{}} {\File{}} {\makestr{a/b}}}.

@@

\begin{figure}
  $$
\begin{array}{lllll}
  \restrictremovefigure{}
\end{array}
  $$
  \caption{Restrict and Remove}
  \label{main:figure:restrictremove}
\end{figure}

>>>>

\paragraph{Logical formulas over type environments}
Standard type systems use type environments to track lexical type information.
Introducing a lexically scoped variable $x$ is a matter of
associating $x$ with its type $\Number$ (a number) in the type environment.
Correspondingly, checking the type of a variable is a simple map lookup.
$$
\begin{array}{lr}
\judgementtwo{\x{} \mapsto \Number}{\appexp{\inc{}}{\x{}}}{\Number}
&
\infer [LC-Local]
{ {\propenv{}}(\x{}) = {\t{}}
}
{ \judgementtwo {\propenv{}} 
            {\x{}} {\t{}}
           }
\end{array}
$$

Occurrence typing takes a different approach.
The same information is conveyed by \emph{logical formulas}.
The logical statement {\isprop{\Number{}}{\x{}}} says the value
obtained via $x$ is of type \Number{}. A \emph{logical system}
must now \emph{prove}
a variable's type.
$$
\begin{array}{lr}
\judgementtwo{\isprop{\Number{}}{\x{}}}{\appexp{\inc{}}{\x{}}}{\Number}
&
\infer [T-LocalProve]
{ \inpropenv {\propenv{}} {\isprop {\t{}} {\x{}}}}
{ \judgementtwo {\propenv{}} 
            {\x{}} {\t{}}
           }
\end{array}
$$
The proof system judgment { \inpropenv {\propenv{}} {\isprop {\t{}} {\x{}}}}
says under logical assumptions {\propenv{}}, variable \x{} is of type \t{}.
%We later define the more general T-Local.

\paragraph{Symbolic representation}
As we saw in \secref{sec:overview},
occurrence typing is capable of reasoning
about deeply nested expressions.
For each expression, the type system assigns a symbolic representation
with respect to the current lexical environment. For example,
\begin{itemize}
  \item variable \makelocal{m} is represented as \makelocal{m}; 
  \item $\appexpone{\ccclass{\appexp{\makekw{lunch}}{\makelocal{m}}}}$ is represented as ${\path{\classpe{}}{\path{\keype{\makekw{lunch}}}{\makelocal{m}}}}$;
  \item $42$ has no representation, called \emptyobject{}.
\end{itemize}
This symbolic representation is called the expression's \emph{object}. 
\figref{main:figure:termsyntax} gives the syntax for objects.
\emptyobject{} is the
\emph{empty object}. Non-empty objects \path{\pathelem{}}{\x{}} consist of a root variable \x{} and a \emph{path} \pathelem{},
a possibly-empty sequence of \emph{path elements} applied right-to-left starting from the root variable.
We use two path elements---{\classpe{}} and {\keype{k}}---representing the result
of a calling \classconst{} and the result of looking up a keyword $k$ respectively.

@@

\paragraph{Logical statements about objects}
So far we have seen logical statements about the simplest object, a variable---{\isprop{\t{}}{\x{}}}---
saying variable \x{} is of type \t{}.
We extend logical statements to reason about \emph{arbitrary} non-empty 
objects {\isprop{\t{}}{\path{\pathelem{}}{\x{}}}}.

To illustrate, recall \egref{example:desserts-on-meal}.
We know the parameter \makelocal{o} is of type $\Order$
by the annotation on $desserts$---written
\begin{equation}
\qquad {\isprop{\Order}{\makelocal{o}}}
\end{equation}
as a logical statement.
%
In checking the ${\makekw{combo}}$ method, we also assume
${\appexp{\makekw{Meal}}{\makelocal{o}}}$ is ${\makekw{combo}}$,
based on multimethod dispatch rules. This is written
\begin{equation}
  \qquad {\isprop{\Value{\makekw{combo}}}{\path{\keype{\makekw{Meal}}}{\makelocal{o}}}}
\end{equation}
and pronounced ``the ${\makekw{Meal}}$ path of variable \makelocal{o} is of type
{\Value{\makekw{combo}}}'', a keyword singleton type.

\paragraph{Logical system in action} 
To attain the type of \makelocal{o}, 
T-LocalProve says we must solve for \t{} in
$
{ \inpropenv 
  {\propenv{}}
  {\isprop {\t{}} {\makelocal{o}}}}
$,
under proposition environment 
$$
\propenv{} = {{\isprop{\Order}{\makelocal{o}}},
    {\isprop{\Value{\makekw{combo}}}{\path{\keype{\makekw{Meal}}}{\makelocal{o}}}}}
$$

The main 
$$
\LUpdatePos
$$
Now the purpose of a logical representation can be conveyed---we rely on the logical
system to combine pieces of type information to deduce more accurate types for lexical
bindings.

\paragraph{Extended to propositional logic}
We extend our logical statements to \emph{propositional logic}.
\figref{main:figure:termsyntax} describes the syntax we will use for the rest of the paper.
The proposition metavariable \prop{} 
consists of positive and negative \emph{type propositions} 
about non-empty objects---{\isprop {\t{}} {\path {\pathelem{}} {\x{}}}}
and {\notprop {\t{}} {\path {\pathelem{}} {\x{}}}}
respectively---the former we have seen before, 
the latter pronounced ``the object {\path {\pathelem{}} {\x{}}} is \emph{not} of type \t{}''.
The other propositions are standard logical connectives: implications, conjunctions,
disjunctions, and the trivial (\topprop{}) and impossible (\botprop{}) propositions.

@@

%The pair of propositions {\filterset{\thenprop{\prop{}}}{\elseprop{\prop{}}}} is called a \emph{proposition set}.

@@

\paragraph{Typing rules}
The core type rules are
given as \figref{main:figure:othertypingrules}. We introduce
the interesting rules while demonstrating how to check
the complement number predicate
\begin{equation}
\abs{\makelocal{d}}{\Top}{\ifexp{\appexp{\numberhuh{}}{\makelocal{d}}}{\false{}}{\true{}}}
\end{equation}
%, including
%a subsumption rule T-Subsume and rules for the false values---T-Nil and T-False---encoded 
%as impossible (\botprop{}) `then' propositions.

The lambda rule T-Abs introduces \isprop{\Top}{\makelocal{d}}
to check the body.
With \propenv{} = \isprop{\Top}{\makelocal{d}},
T-If then checks the test {\appexp{\numberhuh{}}{\makelocal{d}}}
with T-App with three main steps.

First, the operator \numberhuh{} is checked with T-Const, which
uses 
the \constanttypeliteral{} relation to give types to constants.
\numberhuh{} is a predicate over numbers, and
\classconst{} returns its argument's class.
$$
\constanttypefigure{}
$$
The dynamic semantics for constants are given as \figref{main:figure:primitivesem}.

Resuming {\appexp{\numberhuh{}}{\makelocal{d}}},
the operand \makelocal{d} is checked with
T-Local as
$$
\judgementselfrewrite{\propenv{}}
                     {\makelocal{d}}
                     {\UnionNilNum}
                     {\filterset{\notprop{\falsy}{\makelocal{d}}}
                                {\isprop{\falsy}{\makelocal{d}}}}
                     {\makelocal{d}}
$$
which encodes the type, proposition, and object information
previously discussed about variables.

Finally, T-App substitutes the operand's object for the parameter
---here \makelocal{d} for \numberhuh{}'s \x{}---yielding
$$
\judgementselfrewrite{\isprop{\Top}{\makelocal{d}}}{\appexp{\numberhuh{}}{\makelocal{d}}}
  {\Boolean{}}
  {\filterset{\isprop{\Number{}}{\makelocal{d}}}
             {\notprop{\Number{}}{\makelocal{d}}}}
  {\emptyobject{}}
$$

To check {\ifexp{\appexp{\numberhuh{}}{\makelocal{d}}}{\false{}}{\true{}}},
T-If then
introduces \isprop{\Number{}}{\makelocal{d}}
in the `then' branch and \notprop{\Number{}}{\makelocal{d}}
in the `else' branch.
%The object \x{} over latent propositions \thenprop{\prop{}} and
%\elseprop{\prop{}}, latent object \object{}, and latent type \t{}. The
%actual argument object---\objectp{}---is substituted in at application by T-App.

The T-App rule instantiates parameters---like \x{} in T-Abs---with their actual object.
The expression {\appexp{\numberhuh{}}{\makelocal{d}}} replaces its parameter object with \
\judgementselfrewrite{\isprop{\Top}{\makelocal{d}}}{\appexp{\numberhuh{}}{\makelocal{d}}}
  {\Boolean{}}
  {\filterset{\isprop{\Number{}}{\makelocal{d}}}
             {\notprop{\Number{}}{\makelocal{d}}}}
  {\emptyobject{}}

The T-If refines each branch based on the test---a
{\appexp{\numberhuh{}}{\makelocal{d}}} test introduces \isprop{\Number{}}{\makelocal{d}}
for checking the `then' branch and \notprop{\Number{}}{\makelocal{d}}
for checking the `else' branch.
Information from each branch is combined via subsumption for the overall type, propositions, and object.

For example
$
\judgementselfrewrite{\isprop{\Top}{\makelocal{d}}}
  {\ifexp{\appexp{\numberhuh{}}{\makelocal{d}}}{\false{}}{\true{}}}
  {\Boolean{}}
  {\filterset{\notprop{\Number{}}{\makelocal{d}}}
             {\isprop{\Number{}}{\makelocal{d}}}}
  {\emptyobject{}}
$
type checks because T-Subsume allows us to check both branches as
$
\judgementselfrewrite{\isprop{\Number{}}{\makelocal{d}}}
  {\false{}}
  {\Boolean{}}
  {\filterset{\notprop{\Number{}}{\makelocal{d}}}
             {\isprop{\Number{}}{\makelocal{d}}}}
  {\emptyobject{}}
$
and
$
\judgementselfrewrite{\notprop{\Number{}}{\makelocal{d}}}
  {\true{}}
  {\Boolean{}}
  {\filterset{\notprop{\Number{}}{\makelocal{d}}}
             {\isprop{\Number{}}{\makelocal{d}}}}
  {\emptyobject{}}
$
respectively.
%
%For example, if \e{2} is true when variable {\makelocal{y}} is a \File{}
%and \e{3} is true when variable {\makelocal{z}} is a \Number{}, then
%we use T-Subsume on both branches
%to introduce a logical disjunction
%since at least one must be true if the entire expression is true.

@@

\begin{figure*}
$$
\footnotesize
    %{\TDo}
    %{\TClass}
    %{\TIf}
    %{\TAbs}
    %\begin{array}{c}
    %  {\TSubsume}\\\\
    %  {\TNum}
    %\end{array}
  \begin{array}{c}
    {\TLocal} \ \ \  \ \ \ 
    {\TIf}\ \ \  \ \ \ \ \ 
    {\TAbs} \ \ \ \ 
    \begin{array}{c}
      {\TNil}\\\\
      {\TFalse}
    \end{array}
    \\\\
    {\TLet} \ \ \  \ \ \ \ \ \ 
    {\TApp}
    \\\\
    \begin{array}{c}
      {\TNum}\\\\
      {\TConst}
    \end{array} \ \ \ \
    \begin{array}{c}
      {\TKw}\\\\
      {\TNum}\\\\
      {\TClass}
    \end{array} \ \ \ \
    \begin{array}{c}
      {\TSubsume}
    \end{array} \ \ \ \ 
    \begin{array}{c}
      {\TStr}\\\\
      {\TTrue}
    \end{array}
  \end{array}
    %\begin{array}{c}
    %  {\TSubsume}\\\\
    %  {\TStr}\\\\
    %  {\TNil}\\\\
    %  {\TFalse}
    %\end{array}
$$
  \caption{Core typing rules}
  \label{main:figure:othertypingrules}
\end{figure*}

@@

The let rule T-Let links inferred information about
\x{} to the expression used to instantiate \x{}, \ep{1}, via logical implications.

@@

\paragraph{Subtyping}
\figref{main:figure:subtyping} presents subtyping
as a reflexive and transitive relation with top type \Top. 
Singleton types are instances of their respective classes---boolean singleton types
are of type \Boolean{}, class literals are instances of \Class{} and keywords are
instances of \Keyword{}.
Instances of classes \class{} are subtypes of \Object{}. Since function types 
are subtypes of \IFn{}, all types except for \Nil{} are subtypes of \Object{},
so \Top{} = {\Union{\Nil}{\Object}}.
Function subtyping is contravariant left of the arrow---latent propositions, object
and the result type are covariant.
Subtyping for untagged unions is standard.
%The definition of \updateliteral{} supports various idioms relating to \classpe{}
%which we introduce in \secref{sec:isaformal}.

@@

\paragraph{Constructors} First we check and convert {\newexp {\File{}} {\makestr{a/b}}} to {\newstaticexp {\String} {\File{}} {\File{}} {\makestr{a/b}}}
The T-New typing rule checks and rewrites constructors.
$$
    {\TNew}
$$
To check
{\newexp {\File{}} {\makestr{a/b}}}
we first resolve the constructor overload in the class table---there is at most one
to simplify presentation.
With \classhint{1} = \String,
we convert to a nilable type the argument with \t{1} = \Union{\Nil}{\String}
and type check {\makestr{a/b}} against \t{1}.
Typed Clojure defaults to allowing non-nilable arguments, but this
can be overridden, so we model the more general case.
% which erases nil
The return Java type \File is converted to a non-nil
Typed Clojure type \t{} = \File for the return type,
and the propositions say constructors can never be false---constructors
can never produce the internal boolean value that Clojure uses for \false{}, or \nil{}.
Finally, the constructor rewrites to {\newstaticexp {\String} {\File{}} {\File{}} {\makestr{a/b}}}.

@@

%\begin{figure}
%  $$
%\begin{array}{lllll}
%  \restrictremovefigure{}
%\end{array}
%  $$
%  \caption{Restrict and Remove}
%  \label{main:figure:restrictremove}
%\end{figure}
